Evaluative adjective sentences: \\ A question-based analysis of projection

### 2019-07-09 paper/paper-anon.tex
minor edits and comments in response letter and paper

\citealt{tbd-variability} provided experimental evidence for the Gradient Projection Principle on the basis of an experimental investigation 19 projective contents associated with American English expressions. Specifically, \citet{tbd-variability} found a positive correlation between not-at-issueness and projection such that content that is more not-at-issue is also more projective. For instance, as shown in Figure \ref{tbd} for 9 of these 19 contents ($r$ = .85), the prejacent of EASs with {\em stupid} is not only less projective than the content of the complement of {\em know}, but also less not at-issue.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=.9]{/Users/tonhauser.1/Documents/current-research-topics/NSF-NAI/prop-att-experiments/2evaluative-adjectives/content-context-experiment/results/graphs/count-of-participants}

\caption{Histogram of participants in Experiment 1 by their mean projectivity ratings and by whether the truth of the generalization is less likely (left panel) or more likely (right panel) to be taken to follow from the common ground}\label{f-dialect}
\end{center}
\end{figure}

>>>>

\citealt{tbd-variability} provided experimental evidence for the Gradient Projection Principle on the basis of an experimental investigation 19 projective contents associated with American English expressions. Specifically, \citet{tbd-variability} found a positive correlation between not-at-issueness and projection such that content that is more not-at-issue is also more projective. For instance, as shown in Figure \ref{tbd} for 9 of these 19 contents ($r$ = .85), the prejacent of EASs with {\em stupid} is not only less projective than the content of the complement of {\em know}, but also less not at-issue. \jd{the projectivity difference here is real, but is the at-issueness difference significant? those error bars look highly overlapping}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=.9]{figures/count-of-participants}

\caption{Histogram of participants in Experiment 1 by their mean projectivity ratings and by whether the truth of the generalization is less likely (left panel) or more likely (right panel) to be taken to follow from the common ground.	}\label{f-dialect}
\end{center}
\end{figure}
